---
title: "Feather River 2015 Mean Mainstem"
output: html_notebook
---

This set of R scripts processes logger data for predictive stream temperature modeling
Created: 01 Feb 2019
Updated: 01 Mar 2019
USGS station: 11401112

Stage setting:
```{r, message=FALSE}
library(timeSeries)
library(lattice)
library(foreign)
library(doBy)
library(qpcR)
library(pls)
library(boot)
library(Hmisc)
library(readxl)
library(lubridate)
library(zoo)
library(car)
library(gvlma)
library(ggplot2)
library(rgdal)
library(raster)
library(RColorBrewer)
library(classInt)
library(uuid)
```
```{r}
  basin <- "FR"
  midBasin <- "Feather"
  longBasin <- "Feather_River"
  yrPath <- "15"
  yearPath <- "2015"

  nameBasin <- "Feather" #this is from the Projects XML list of approved names
  
  
  mainPath <- "D:/OneDrive/work/research/CHaMP/CHaMP_data/"
  metricPath <- "D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/metrics"
  
  var <- "Mn"
  longVar <- "Mean"
  dataVar <- "Mn8D" #name of the variable in the logger data
  capVar <- "MEAN"
  
  modelPath <- "D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/Mainstem/2015/Mean/"
  gisPath <- "D:/OneDrive/work/research/CHaMP/GIS/coverages/"
  
```
This part reads the LST data and gap-fills using a cubic spline function
```{r, message=FALSE}

  LST.in <- read.csv("D:/OneDrive/work/research/CHaMP/GIS/coverages/Feather_River/FR_15_LST.csv")
  PointID <- LST.in[,1]
  LST.in <- LST.in[,2:47]
  LST.in[LST.in<0.1] = NA
  
  LST.names<-colnames(LST.in)
  
  myFunc <- function(x)
    {
      if (is.na(x[1]))
      {
        x[1] <- 13022
      }
      x
    }
  
  LST.filled <- apply(LST.in, 1, function(x) myFunc(x))
  LST.filled <- as.data.frame(t(LST.filled))
  
  
  myFunc2 <- function(x)
    {
      if (is.na(x[46]))
      {
        x[46] <- x[43]
      }
      x
    }
  
  
  LST.filled <- apply(LST.filled, 1, function(x) myFunc2(x))
  LST.filled <- as.data.frame(t(LST.filled))
  
  myFunc3 <- function(x)
    {
      if (is.na(x[46]))
      {
        x[46] <- 12943
      }
      x
    }
  
  LST.filled <- apply(LST.filled, 1, function(x) myFunc3(x))
  LST.filled <- as.data.frame(t(LST.filled))
  
  tLST.in <- t(LST.filled)
  
  tLST.out <- na.spline(tLST.in)
  CLST <- tLST.out*0.2-273.15
  tCLST <- t(CLST)
  CLST.out <- as.data.frame(tCLST)
  
    
  CLST.out$PointID <- PointID
  colnames(CLST.out)[1:46] <- LST.names
```
Plot to look
```{r}
  plot(1:46, CLST.out[1,1:46])
  plot(1:46, CLST.out[100,1:46])
```
```{r}
  
  write.dbf(CLST.out, file = paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/LST15_FR_interp.dbf"))
  
  
```
This part calculates the zonal mean of the daily LST for each RCA
```{r}
out_Preds <- read.dbf("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/LST15_FR_interp.dbf")
  
  
  weights <- read.csv("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/FR_rca_area_wgts.csv")
  weights[weights$area_wgt<0.01, "area_wgt"] = 0.01
  colnames(weights)[1] <- "RCAID"
  rcas <- unique(unlist(weights$RCAID))
  rca_zonal <- matrix(ncol=46, nrow=length(rcas))
  
  
  l <- 1
  
  for(i in rcas)	
    {
      pixels <- weights[weights$RCAID == i, "GRIDCODE"]
      wgts <- weights[weights$RCAID == i, "area_wgt"]
      
      for (j in 1:46)
      {
        daily <- out_Preds[out_Preds$PointID %in% pixels, j]
        zonal_mn <- weighted.mean(daily, wgts, na.rm = TRUE)
        rca_zonal[l,j] <- zonal_mn
      }
      l <- l+1
    }
  
  
  colnames(rca_zonal)[1:46] <- colnames(out_Preds)[1:46]
  rca_zonal <- as.data.frame(rca_zonal)
  rca_zonal$RCAID <- rcas
```
Plot to look
```{r}
  plot(1:46, rca_zonal[1,1:46])
  plot(1:46, rca_zonal[100,1:46])
  write.dbf(rca_zonal, file = paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/LST15_FR_RCA.dbf"))
  
```
Discharge data formatting
```{r}

  Dv.in <- read.csv("D:/OneDrive/work/research/CHaMP/CHaMP_Data/Feather/Mainstem/2015/FR_dv_data_2015_main.csv", stringsAsFactors = FALSE)
  
  dates <- matrix(nrow=365, ncol=1)
  dates[,1] <- 1:365
  colnames(dates) <- c("Days")
  
  SiteID <- unique(Dv.in$site_no)
  SiteID <- as.matrix(SiteID)
  Dv.8Day.out <- data.frame (mup = NULL)
  
  for (i in SiteID) 
    { 
      Dv.site <- Dv.in[Dv.in$site_no == i,]
      full.year <- merge(dates, Dv.site, by.x = "Days", by.y = "JulDay", all.x = TRUE)
      eightday <- rollapply(full.year$Dv, width = 8, FUN = mean, na.rm = T, fill = NA, align = c("left"))
      eightday <- as.matrix(eightday)
      full.year$Dv8D<- eightday
      full.year$Dv8D[361] <- mean(full.year$Dv[361:365 ])
      Dv.8Day.out <- rbind(Dv.8Day.out, full.year)
      
    }
  
  ind <- apply(Dv.8Day.out, 1, function(x) !any(is.na(x)))
  Dv.8Day.out <- Dv.8Day.out[ind,]

write.csv(Dv.8Day.out, paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/FR_2015_Dv_8Day_main", ".csv"), row.names = FALSE)

```
Model building. Builds complete (no NA) dataset with discharge, elevation, LST, JulDay.  Splits data into spring and fall with the max temp of the year.
```{r}
  Log.in <- read.csv("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/FR_logger_8D_2015_mainstem.csv", stringsAsFactors = FALSE)
 

  ID.in <- read.csv("D:/OneDrive/work/research/CHaMP/GIS/coverages/Feather_River/FR_sites_rca_2015_main.csv", stringsAsFactors = FALSE) 
  
  LST.in <- read.dbf(paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/LST15_FR_RCA.dbf"))
  colnames(LST.in)<-gsub("X", "", colnames(LST.in))
  newnamesnum <- as.numeric(colnames(LST.in)[1:46]);
  Dv.in <- read.csv("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/FR_2015_Dv_8Day_main.csv", stringsAsFactors = FALSE)
  
  Dv.in <- Dv.in[,c("Dv8D", "Days")]
  
  LST.Log.out <- data.frame (mup = NULL)
  SiteID <- unique(Log.in$SiteName)
  
  for (i in SiteID) 
    { 
      Log.site <- Log.in[Log.in$SiteName  == i,]
      Log.site <- as.data.frame(Log.site)
      
      RCAID <- ID.in$RCAID[ID.in$SiteName == i]
      
      Elev <- ID.in$Elev[ID.in$SiteName == i]
      
      LST.site <- matrix(ncol=3, nrow=46)
      LST.site[,1] <- as.numeric(unlist(colnames(LST.in)[1:46]))
      LST.site[,2] <- unlist(LST.in[LST.in$RCAID == RCAID, 1:46])
      LST.site <- data.frame(LST.site)
      colnames(LST.site) <- c("JulDay", "LST", "Elev")
      LST.site[3] <- Elev
   
      
      LST.Log.site <- merge(LST.site, Log.site, by = "JulDay", all.x=TRUE, all.y = FALSE)
      LST.Log.site <- merge(LST.Log.site, Dv.in, by.x = "JulDay", by.y = "Days", all.x=TRUE, all.y+FALSE)
      
      LST.Log.out <- rbind(LST.Log.out, LST.Log.site)
      
    }
  
  Dv <- unlist(LST.Log.site$Dv8D)
 
  ind <- apply(LST.Log.out, 1, function(x) !any(is.na(x)))
  NoNA.xyz <- LST.Log.out[ind,]
  
  NoNA.xyz <- NoNA.xyz[,c(dataVar, "LST", "JulDay", "Elev", "Dv8D", "SiteName")]
  colnames(NoNA.xyz) <- c("y", "x", "z", "e", "d", "SiteName")
  
  write.csv(x=NoNA.xyz, file= paste0(basin, "_mainstem", yearPath, "_8Day_", var, "_model_data_main.csv"), row.names = FALSE)
  NoNA.xyz <- read.csv(paste0(basin, "_mainstem", yearPath, "_8Day_", var, "_model_data_main.csv"), stringsAsFactors = FALSE)
  
  NoNA.xyz <- orderBy(~z, NoNA.xyz)
  maxrow <- which.max(NoNA.xyz$y)
  data.sp <- NoNA.xyz[1:(maxrow-1),]
  rownames(data.sp) <- 1:dim(data.sp)[1]
  data.fall <- NoNA.xyz[maxrow:nrow(NoNA.xyz),]
  rownames(data.fall) <- 1:dim(data.fall)[1]
```
Correlation matrix
```{r}
cor.full <- NoNA.xyz[1:5]
cor(cor.full)
```
plot the data
```{r}
  {plot(NoNA.xyz$x, NoNA.xyz$y, main = "full year")
  points(data.sp$x, data.sp$y, pch=16, col="cadetblue3")
  points(data.fall$x, data.fall$y, pch=16, col="chocolate")}
  
```

####Full year models
```{r}
  y <- NoNA.xyz$y
  x <- NoNA.xyz$x
  z <- NoNA.xyz$z
  e <- NoNA.xyz$e
  d <- NoNA.xyz$d
  m <- NoNA.xyz$m
  
  mod <- lm(y ~ x + I(x^2) + z+ e)
  sum_mod <- summary(mod)
  sum_mod
``` 
Model prediction
```{r}
  pred.y <- predict(mod)
  {plot(pred.y, y, main = paste0("8-day ", var, " Full Year"))
  abline(0,1)}
```
Model diagnostics
```{r}
  post_mod <- summary(lm(y ~ pred.y))
  gvmodel <- gvlma(mod)
  summary(gvmodel)
```
```{r}
  outlierTest(mod)
```

recheck assumptions
```{r}
  gvmodel <- gvlma(mod)
  summary(gvmodel)
```
```{r}
  qqPlot(mod, main="QQ Plot Full Year")
```
Assumptions:
```{r}
plot(mod)
```
```{r}
  spreadLevelPlot(mod)
```
```{r}
  plot(pred.y, mod$residuals, main="Model diagnostics Full Year", xlab="Predicted", ylab="Residuals")
```
```{r}
  pressstat_sum <- PRESS(mod, verbose = "FALSE")
  RMSEP <- sqrt(mean((pressstat_sum$residuals)^2))
  
  library(pls)
  mod2 <- plsr(y ~ x + I(x^2) + z + e, validation = "LOO")
  p2 <- R2(mod2)
  detach("package:pls", unload=TRUE)
  
  coeffs <- as.matrix(coefficients(sum_mod))
  
  pred.out <- matrix(nrow=length(pred.y), ncol=5)
  pred.out[,1] <- y
  pred.out[,2] <- pred.y
  pred.out[,3] <- z
  pred.out[,4] <- "full year"
  pred.out[,5] <- yearPath
  colnames(pred.out) <- c("Y", "PredY", "JulDay", "Season", "Year")
  write.table (x=pred.out,append=T,row.names=F,file=paste0("jk_pred_v_y_", var, "_", basin, "_mainstem", yearPath, "_full_year.csv"),sep = ",", col.names=F)  
  
```
```{r}  
  fit <- lm(y~ pred.y)
  
  summary(fit)
```
Output tables formatting for coeffs and metrics
```{r}    
  coeffs_out <- data.frame(Int=numeric(2), bLST=numeric(2), bLST2=numeric(2), bJul=numeric(2), bElev=numeric(2), bD=numeric(2))
  metrics_out <- data.frame(r2=numeric(2), RMSE=numeric(2), p2=numeric(2), RMSEP=numeric(2), N_Sites=numeric(2), N=numeric(2))
  rownames(metrics_out) <- c("Spring", "Fall")
  rownames(coeffs_out) <- c("Spring", "Fall")

  coeffs_out[1,1] <- coeffs[1,1]
  coeffs_out[1,2] <- coeffs[2,1] 
  coeffs_out[1,3] <- coeffs[3,1]
  coeffs_out[1,4] <- coeffs[4,1]
  coeffs_out[1,5] <- coeffs[5,1]
 
  
  metrics_out[1,1] <- sum_mod$adj.r.squared
  metrics_out[1,2] <- sum_mod$sigma
  metrics_out[1,3] <- p2$val[5]
  metrics_out[1,4] <- RMSEP
  metrics_out[1,5] <- length(unique(NoNA.xyz$SiteName))
  metrics_out[1,6] <- length(y)
  
  coeffs_out[2,1] <- coeffs[1,1]
  coeffs_out[2,2] <- coeffs[2,1]
  coeffs_out[2,3] <- coeffs[3,1]
  coeffs_out[2,4] <- coeffs[4,1]
  coeffs_out[2,5] <- coeffs[5,1]

  
  metrics_out[2,1] <- sum_mod$adj.r.squared
  metrics_out[2,2] <- post_mod$sigma
  metrics_out[2,3] <- p2$val[5]
  metrics_out[2,4] <- RMSEP
  metrics_out[2,5] <- length(unique(NoNA.xyz$SiteName))
  metrics_out[2,6] <- length(y)
  
  
  write.table(x=coeffs_out, append=F,row.names=T, file = paste0("All_data_", basin, "_mainstem", yearPath, "_mod_coeffs_", var, ".csv"), sep = ",", col.names=T)
  
  write.table(x=metrics_out, append=F,row.names=T, file = paste0("All_data_", basin, "_mainstem", yearPath, "_mod_metrics_", var, ".csv"), sep = ",", col.names=T)
  
```
####Spring/Fall models
Spring data model
```{r}
  coeffs_out <- data.frame(Int=numeric(2), bLST=numeric(2), bLST2=numeric(2), bJul=numeric(2), bElev=numeric(2), bD=numeric(2), bDJul=numeric(2), bJulm=numeric(2), bm=numeric(2))
  metrics_out <- data.frame(r2=numeric(2), RMSE=numeric(2), p2=numeric(2), RMSEP=numeric(2), N_Sites=numeric(2), N=numeric(2))
  rownames(metrics_out) <- c("Spring", "Fall")
  rownames(coeffs_out) <- c("Spring", "Fall")
```
```{r}
  y <- data.sp$y
  x <- data.sp$x
  z <- data.sp$z
  e <- data.sp$e
  d <- data.sp$d
  m <- data.sp$m
  plot(x, y, main="Spring data")
```
```{r}
  mod <- lm(y ~ x + I(x^2) + z + e)
  sum_mod <- summary(mod)
  sum_mod
```
####Model diagnostics
```{r}
  pred.y <- predict(mod)
  pred.y[pred.y < -0.5] = -0.5
  {plot(pred.y, y, main = paste0("8-day ", var, " Spring Leg"))
  abline(0,1)}
```
Test assumption of linear model
```{r}
  post_mod <- summary(lm(y ~ pred.y))
  gvmodel <- gvlma(mod)
  summary(gvmodel)
```
check for outliers
```{r}
  outlierTest(mod)
```

recheck assumptions
```{r}
  gvmodel <- gvlma(mod)
  summary(gvmodel)
```
more tests: qqplot
```{r}
  qqPlot(mod, main="QQ Plot Spring Leg")
```

format the data for prediction output 
```{r}
  
  coeffs <- as.matrix(coefficients(mod))
  pred.y <- predict(mod)
  
  pred.y[pred.y < -0.5] = -0.5
```
Look at the residuals
```{r}
  spreadLevelPlot(mod)
```
LOO PRESS stats
```{r, message=FALSE}
  pressstat_sum <- PRESS(sum_mod, verbose = "FALSE")
  RMSEP <- sqrt(mean((pressstat_sum$residuals)^2))
  
  library(pls)
  mod2 <- plsr(y ~ x + I(x^2) + z + e, validation = "LOO")
  p2 <- R2(mod2)
  detach("package:pls", unload=TRUE)
```
write out predicted, coeffs, & metrics
```{r}
  
  pred.out <- matrix(nrow=length(pred.y), ncol=5)
  pred.out[,1] <- y
  pred.out[,2] <- pred.y
  pred.out[,3] <- z
  pred.out[,4] <- "Spring"
  pred.out[,5] <- yearPath
  colnames(pred.out) <- c("Y", "PredY", "JulDay", "Season", "Year")
  write.table (x=pred.out,append=F,row.names=F,file=paste0("jk_pred_v_y_", var, "_", basin, "_mainstem", yearPath, "_sp_fall.csv"),sep = ",", col.names=F)  
  
  coeffs_out[1,1] <- coeffs[1,1]
  coeffs_out[1,2] <- coeffs[2,1]
  coeffs_out[1,3] <- coeffs[3,1]
  coeffs_out[1,4] <- coeffs[4,1]
  coeffs_out[1,5] <- coeffs[5,1]


  metrics_out[1,1] <- sum_mod$adj.r.squared
  metrics_out[1,2] <- sum_mod$sigma
  metrics_out[1,3] <- p2$val[5]
  metrics_out[1,4] <- RMSEP
  metrics_out[1,5] <- length(unique(data.sp$SiteName))
  metrics_out[1,6] <- length(y)
```
Fall data model
```{r}
  
  y <- data.fall$y
  x <- data.fall$x
  z <- data.fall$z 
  e <- data.fall$e
  d <- data.fall$d
  m <- data.fall$m
  
  plot(x, y, main="fall")
```
```{r}
  mod <- lm(y ~ x + I(x^2) + z + e)
  sum_mod <- summary(mod)
  sum_mod
```
####Model Diagnostics
plot predicted v observed
```{r}
  pred.y <- predict(mod)
  pred.y[pred.y < -0.5] = -0.5
  {plot(pred.y, y, main = paste0("8-day ", var, " Fall Leg"))
  abline(0,1)}
```
Tests of assumptions of linear model
```{r}
  gvmodel <- gvlma(mod)
  summary(gvmodel)
```
check for outliers
```{r}
  outlierTest(mod)
```
recheck assumptions
```{r}
  gvmodel <- gvlma(mod)
  summary(gvmodel)
```
plot model diagnostics
```{r}
  plot(mod)
```

more diagonstics: qqplot
```{r}
  qqPlot(mod, main="QQ Plot Fall Leg")
```

format data for prediction output
```{r}
  coeffs <- as.matrix(coefficients(mod))
  post_mod <- summary(lm(y ~ pred.y)) 
```
LOO PRESS stats
```{r, message=FALSE}
  pressstat_sum <- PRESS(sum_mod, verbose = "FALSE")
  RMSEP <- sqrt(mean((pressstat_sum$residuals)^2))
  
  library(pls)
  mod2 <- plsr(y ~ x + I(x^2) + z+ e, validation = "LOO")
  p2 <- R2(mod2)
  detach("package:pls", unload=TRUE)
```
write out predicted, coeffs, & metrics
```{r}
  pred.out <- matrix(nrow=length(pred.y), ncol=5)
  pred.out[,1] <- y
  pred.out[,2] <- pred.y
  pred.out[,3] <- z
  pred.out[,4] <- "fall"
  pred.out[,5] <- yearPath
  
  write.table (x=pred.out,append=T,row.names=F,file=paste0("jk_pred_v_y_", var, "_", basin, "_mainstem", yearPath, "_sp_fall.csv"),sep = ",", col.names=F)  
  
  coeffs_out[2,1] <- coeffs[1,1]
  coeffs_out[2,2] <- coeffs[2,1]
  coeffs_out[2,3] <- coeffs[3,1]
  coeffs_out[2,4] <- coeffs[4,1]
  coeffs_out[2,5] <- coeffs[5,1]




  
  metrics_out[2,1] <- sum_mod$adj.r.squared
  metrics_out[2,2] <- post_mod$sigma
  metrics_out[2,3] <- p2$val[5]
  metrics_out[2,4] <- RMSEP
  metrics_out[2,5] <- length(unique(data.fall$SiteName))
  metrics_out[2,6] <- length(y)

  
  write.table(x=coeffs_out, append=F,row.names=T, file = paste0("All_data_", basin, "_mainstem", yearPath, "_mod_coeffs_", var, ".csv"), sep = ",", col.names=T)
  
  write.table(x=metrics_out, append=F,row.names=T, file = paste0("All_data_", basin, "_mainstem", yearPath, "_mod_metrics_", var, ".csv"), sep = ",", col.names=T)
  
```
plot the full year of predicted v observed
```{r}
  pred.y <- read.csv(paste0("jk_pred_v_y_", var, "_", basin, "_mainstem", yearPath, "_full_year.csv"), stringsAsFactors = FALSE, header = FALSE)
  colnames(pred.y) <- c("Y", "PredY", "JulDay", "Season", "Year")
  
  {plot(pred.y$PredY, pred.y$Y, pch=16, col="blue", main=paste0(var, " 8-day stream temp ", basin, " ", yearPath), xlab="Predicted", ylab="Observed")
  abline(0,1)
  abline(lm(pred.y$Y~ pred.y$PredY), col="blue")}
```
full year fit metrics
```{r}
  fit <- lm(pred.y$Y~ pred.y$PredY)
  
  summary(fit)
```
This part applies the model coefficients to the LST to generate 8-day temp estimates 
```{r}
  
  elev.in <- read.csv(paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/FR_rca_elev.csv"), stringsAsFactors = F)
  
  LST.in <- read.dbf(paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/LST15_FR_RCA.dbf"))
  
  colnames(LST.in)<-gsub("X", "", colnames(LST.in))
  
  newnamesnum <- as.numeric(colnames(LST.in)[1:46])
  
  LST.elev <- merge(LST.in, elev.in, by = "RCAID")
  
  coeffs.in <- read.csv(paste0("All_data_", basin, "_mainstem", yearPath, "_mod_coeffs_", var, ".csv"), stringsAsFactors=FALSE)
  LogPred.out <- LST.elev[,c(2:47,48,1)]
  LogPred.out[,1:46] <- 0
  rcas <- unique(LST.elev$RCAID)
  LST.sum <- LST.elev[,c(2:47, 48,1)]
  

   for (i in 1:length(rcas))  
      {
        x <- unlist(LST.sum[i,])
        maxrow <- 29 #as.numeric(which.max(x[1:46]))
        midrow <- maxrow - 1
        day <- as.numeric(colnames(LST.sum)[maxrow])
        
        j <- 1
        for (l in 1:midrow)
        {x[l] <- x[l] * coeffs.in$bLST[1] + j * coeffs.in$bJul[1] +  x[47] * coeffs.in$bElev[1] + x[l]^2 * coeffs.in$bLST2[1] + coeffs.in$Int[1]
        j <- j + 8}
        k <- day
        for (l in maxrow:46)     
        {x[l] <- x[l] * coeffs.in$bLST[2] + k * coeffs.in$bJul[2] +  x[47] * coeffs.in$bElev[2] + x[l]^2 * coeffs.in$bLST2[2] + coeffs.in$Int[2]
        k <- k + 8}
        if (maxrow > 3)
        {
          x[(midrow)] <- NA
          fill <- na.spline(x[1:46],)
          x[(maxrow-3):(maxrow+3)] <- fill[(maxrow-3):(maxrow+3)]
        }
        LogPred.out[i,1:46] <- x [1:46] 
      }
    
  
  LogPred.out <- as.data.frame(LogPred.out)
  
  LogPred.out$Basin_RCA <- paste0(basin, "_mainstem", LogPred.out$RCAID)
  namesnum <- as.numeric(colnames(LogPred.out[1:46]))
  varName <- paste0("T", var, yrPath)
  names.out <- sprintf("%s_%03d", varName, namesnum)
  colnames(LogPred.out)[1:46] <- names.out[1:46]
  LogPred.out[LogPred.out < -0.5] = -0.5
  
  write.dbf(LogPred.out, file = paste0("predt", yearPath, "_", basin, "mainstem_8D_", var, ".dbf"))
```
Plot orig data
```{r}
  plot(NoNA.xyz$z, NoNA.xyz$y)
```
Plot some reaches to take a peek
```{r}  
  {plot(namesnum, LogPred.out[1,1:46])
  points(namesnum, LogPred.out[10, 1:46], pch=16, col="blue")
  points(namesnum, LogPred.out[150, 1:46], pch=16, col="green")
  points(namesnum, LogPred.out[200, 1:46], pch=16, col="red")
  points(namesnum, LogPred.out[100, 1:46], pch=16, col="lightgreen")
  points(namesnum, LogPred.out[80, 1:46], pch=16, col="lightblue")}
  
```
This parts formats the error by day/site info

```{r}

  Log.in <- read.csv(paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/Feather/mainstem/2015/FR_logger_8D_2015_mainstem.csv"), stringsAsFactors = FALSE)
  
  ID.in <- read.csv(paste0("D:/OneDrive/work/research/CHaMP/GIS/coverages/Feather_River/FR_sites_rca_2015_main.csv"), stringsAsFactors = FALSE) 
  
  
  Pred.in <- read.dbf(paste0("predt", yearPath, "_", basin, "mainstem_8D_", var, ".dbf"))
  colnames(Pred.in)<-gsub(varName, "", colnames(Pred.in))
  colnames(Pred.in)<-gsub("_", "", colnames(Pred.in))
  newnamesnum <- as.numeric(colnames(Pred.in)[1:46]);
  
  Pred.Log.out <- data.frame (mup = NULL)
  SiteID <- unique(Log.in$SiteName)

    for (i in SiteID) 
      { 
        Log.site <- Log.in[Log.in$SiteName  == i,]
        Log.site <- as.data.frame(Log.site)
        
        
        RCAID <- ID.in$RCAID[ID.in$SiteName == i]
        
        Pred.site <- matrix(ncol=2, nrow=46)
        Pred.site[,1] <- as.numeric(unlist(colnames(Pred.in)[1:46]))
        Pred.site[,2] <- unlist(Pred.in[Pred.in$RCAID == RCAID,1:46])
        Pred.site <- data.frame(Pred.site)
        colnames(Pred.site) <- c("JulDay", "Pred")
        
        Pred.Log.site <- merge(Pred.site, Log.site, by.x = "JulDay",by.y = "JulDay", all.x=TRUE, all.y = FALSE)
        
        Pred.Log.out <- rbind(Pred.Log.out, Pred.Log.site)
      }

  ind <- apply(Pred.Log.out, 1, function(x) !any(is.na(x)))
  NoNA.pred <- Pred.Log.out[ind,]
  
  NoNA.pred <- NoNA.pred[,c(dataVar, "Pred", "JulDay", "SiteName")]
  colnames(NoNA.pred) <- c("Obs", "Pred", "JulDay", "SiteName")
  

  SiteID <- unique(NoNA.pred$SiteName)
  SiteID <- as.matrix(SiteID)
  Error.pts.out <- matrix(nrow = length(SiteID), ncol = 47)
  
  errorName <- paste0("JulDay_", namesnum)
  colnames(Error.pts.out)[2:47] <- errorName
  colnames(Error.pts.out)[1] <- "SiteName"
  
  Error.pts.out[1:length(SiteID), 1] <- unlist(SiteID)[1:length(SiteID)]
  Error.pts.out <- as.data.frame(Error.pts.out, stringsAsFactors = FALSE)


    for (i in SiteID) 
      { 
        error.site <- NoNA.pred[NoNA.pred$SiteName  == i,]
        error.site$error <- error.site[,'Obs']-error.site[,'Pred']
        
        
        error <- matrix(ncol=1, nrow=46)
        error[,1] <- namesnum
        error <- data.frame(error)
        colnames(error) <- c("JulDay")
        
        error.site.fill <- merge(error, error.site, by = "JulDay", all.x=TRUE, all.y = FALSE)
        Error.pts.out[Error.pts.out$SiteName==i,2:47] <- as.numeric(unlist(error.site.fill$error))
      }

  Error.pts.out[,2:47] <- sapply(Error.pts.out[,2:47], as.numeric)
  
  Error.pts.out[,2:47] <- round(Error.pts.out[,2:47], digits=3)

write.dbf(Error.pts.out, file = paste0("Error", yearPath, "_", basin, "mainstem_8D_", var, ".dbf")) 
write.csv(Error.pts.out, file = paste0("Error", yearPath, "_", basin, "mainstem_8D_", var, ".csv"), row.names = FALSE)
```
Geospatial data output
```{r}

  gisPath <- paste0("D:/OneDrive/work/research/CHaMP/GIS/coverages/", longBasin)
  
  netname <- paste0("NHD_NFEF_Final_RCA_mainstem_20190312")
  ptsname <- paste0("TempSites_2015_mainstem")
  
  error_pts <- readOGR(dsn=gisPath, ptsname)
  error_pts@data <- error_pts@data[,c("SiteName", "RCAID")]
  
  network <- readOGR(dsn=gisPath, layer = netname)
  network@data <- network@data[,c("RCAID", "SegmentID")]
  colnames(network@data)[1] <- "RCAID"
  
  network <- spTransform(network, proj4string(error_pts))
  
  error_pts <- merge(error_pts, Error.pts.out, by.x="SiteName", by.y="SiteName")
  network <- merge(network, LogPred.out, by = "RCAID")                    
                    
  outnetname <- paste0(basin, "_mainstem", yearPath, "_8D_", var)
  outptsname <- paste0(basin, "_Error_mainstem_", yearPath, "_8D_", var)
  
  writeOGR(obj=error_pts, dsn=".", layer = paste0(outptsname), driver="ESRI Shapefile", overwrite_layer = TRUE)
  writeOGR(obj=network, dsn=".", layer = paste0(outnetname), driver="ESRI Shapefile", overwrite_layer = TRUE)
```
Animation output
```{r}

  seis = c("#480000","#5e0000","#770000","#910000", "#AA0000", "#D00000", "#F70000", "#FF1D00", "#FF4400", "#FF6A00", "#FF9000", "#FFB700", "#FFDD00", "#FFE200", "#BDFF0C", "#73FF1A", "#3FFA36", "#16F45A", "#00D08B", "#0087CD", "#0048FA", "#0024E3")
  seis <- rev(seis)

  network@data$SegmentID <- as.numeric(network@data$SegmentID)

  names.out <- colnames(network@data[3:48])
  namesnum <- as.numeric(gsub(paste0("T", var, yrPath, "_"), "", colnames(network@data[3:48])))
  means <- colMeans(network@data[3:48], na.rm = TRUE)
  SDs <- colStdevs(network@data[3:48], na.rm = TRUE)
  yplus <- means + SDs
  yminus <- means - SDs
  df <- data.frame(means=means, SDs=SDs, names=namesnum)
  sequ <- c(1:46)
  namer <- sprintf('%03d', sequ)
  fix4 <- classIntervals(means, n = 14, style = "fixed",fixedBreaks=c(-1,2,4,6,8,10,12,14,16,18,20,22,24,26))
  fix4.colors <- findColours(fix4,pal=seis)
```
loops through and writes out the graphics
```{r}

  for (i in 3:48)
    {
      
      namey <- gsub(paste0("T", var, yrPath, "_"), "", colnames(network@data)[i])
      
      filename <- paste0(modelPath, "graphics/", namer[i-2], ".png", sep="")
      png(filename=filename, res = 300, width = 1500, height = 1500, units = "px", bg="black")
      
      u <- unique(network@data[,i])
      
      if(length(u )< 3){ 
        fix3.colors <- rep("#0024E3",282)
      } else {
      fix3 <- classIntervals(network@data[,i], n = 15, style = "fixed",fixedBreaks=c(-1,2,4,6,8,10,12,14,16,18,20,22,24,26))
      fix3.colors <- findColours(fix3,pal=seis)
      }

      cexEr <-ifelse(abs(error_pts@data[,i]) == 0, 0,
                     ifelse(abs(error_pts@data[,i])>0 & error_pts@data[,i-1]<1, 0.5,
                            ifelse(abs(error_pts@data[,i])>1 & error_pts@data[,i-1]<2, 0.75,
                                   ifelse(abs(error_pts@data[,i])>2 & error_pts@data[,i]<3, 1.0,
                                          ifelse(abs(error_pts@data[,i])>3, 1.25,
                                                 ifelse(abs(error_pts@data[,i])== NA, 0, NA))))))
      
      plot(network, col=fix3.colors, bg="black", fg="white")
      points(error_pts, pch=16, col="gray40", cex=cexEr)
      
       legend(x=grconvertX(c(0.85,0.9), from='npc'), 
        y=grconvertY(c(0.3, 0.5), from='npc'), fill = c("#0024E3", "#0087CD", "#16F45A", "#3FFA36", "#BDFF0C", "#FFDD00", "#FF9000", "#FF4400", "#F70000", "#AA0000", "#910000","#770000","#5e0000", "#480000"), legend = c("0-2","2-4","4-6","6-8","8-10","10-12","12-14","14-16","16-18","18-20", "20-22","22-24","2-26",">26"), bty = "n", cex=.5, inset=c(.1,0), text.col="white");
        
       legend("topright", pch=16, col="gray40", pt.cex=c(0.5, 0.75, 1.0, 1.25), title="Model error (°C)", legend = c("0-1","1-2","2-3","3+"), bty = "n", cex=.5, inset=c(0,0), text.col="white");
        
      
      
      title(paste0(nameBasin, " 8-day ", longVar, " ", yearPath, " (°C)"), line=-0.6, adj=0, col.main="white", col.sub="white", outer=FALSE, cex.main=0.5)
      mtext(paste0("Julian Day ", namey),side =1, outer=TRUE, line=-5, col="white", cex=.5)
      
      tmp2 <- subplot(
        plot(namesnum[1:(i-2)], means[1:(i-2)], col=fix4.colors, pch=16, bty="n", xlim=c(0,360), ylim=c(0,27), cex.main=.8, main="Basin mean (+/-SD)", adj=0, xlab='',ylab='', col.lab="white", cex.axis=0.5, cex.lab = 0.25, col.axis="white", col.main = "white", bg="black"), 
        x=grconvertX(c(0.40,0.80), from='npc'), 
        y=grconvertY(c(0.05, 0.20), from='npc'),
        size=c(1,1.5), vadj=0.5, hadj=0.5, 
        pars=list( mar=c(0,0,0,0)+0.1, cex=0.5))
      op <- par(no.readonly=TRUE)
      par(tmp2)
      arrows(namesnum[1:(i-2)], yplus[1:(i-2)], namesnum[1:(i-2)], yminus[1:(i-2)], length=0, lwd=5, code=3, lend=0, col="gray20")
      par(op)
      tmp2 <- subplot(
        plot(namesnum[1:(i-2)], means[1:(i-2)], col=fix4.colors, pch=16, bty="n", xlim=c(0,360), ylim=c(0,27), cex.main=.8, main="Basin mean (+/-SD)", adj=0, xlab='',ylab='', col.lab="white", cex.axis=0.5, cex.lab = 0.25, col.axis="white", col.main = "white", bg="black"), 
        x=grconvertX(c(0.40,0.80), from='npc'), 
        y=grconvertY(c(0.05, 0.20), from='npc'),
        size=c(1,1.5), vadj=0.5, hadj=0.5, 
        pars=list( mar=c(0,0,0,0)+0.1, cex=0.5))
      
      dev.off()
    }
    
    
  
```
This system call builds an mpeg out of the still graphics
```{r, message=FALSE, warning=FALSE}
setwd(paste0(modelPath, "/graphics/"))
  
  system('"C:/Program Files/ImageMagick-7.0.1-Q16/convert.exe" -delay 20 -morph 3 *.png FR_2015_8D_Mn_mainstem.mpeg')
```
