  ---
title: "Code to output fishy map animations"
output: html_notebook
---

This set of R scripts reads in stream temperature estimates and outputs threshold animations for either CHNK or STHD stream extents
Created: 31 Jan 2018
Used for all watersheds and all years by changing the basin names and year paths 
Parameters for:
  CHNK Adult holding/spawning 20' mx, 1 July - 30 Sept (161-281)
  sequ <- c(1:80)
  i in:  2011 1:16, 2012 17:32, 2013 33:48, 2014 49:64, 2015 65:80, 2016 81:96
Package loads:
```{r, message=FALSE}
library(timeSeries)
library(lattice)
library(foreign)
library(doBy)
library(qpcR)
library(pls)
library(boot)
library(Hmisc)
library(readxl)
library(lubridate)
library(zoo)
library(car)
library(gvlma)
library(ggplot2)
library(rgdal)
library(raster)
library(RColorBrewer)
library(classInt)
library(uuid)
library(plyr)
```
Stage setting
```{r, message=FALSE, warning=TRUE}
  
  basin <- "Ent"
  
  longBasin <- "Entiat"
  nameBasin <- "Entiat"
  
  mainPath <- paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/") 
  otherOutPath <- paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/FishMap/", longBasin, "/")
  
  
  var <- "Mx"
  longVar <- "Max"
  
  
  gisPath <- paste0("D:/OneDrive/work/research/CHaMP/GIS/coverages/", longBasin)
  
  namer <- c(1,9,17,25,33,41,49,57,65,73,81,89,97,105,113,121,129,137,145,153,161,169,177,185,193,201,209,217,225,233,241,249,257,265,273,281,289,297,305,313,321,329,337,345,353,361)
  namey <- sprintf('%03d', namer)
```
Parsing network extent
```{r}
 rcaName <- paste0(basin, "_STHD_net")
    rca <- readOGR(dsn=gisPath, layer = rcaName)
    rcas <- rca@data
    rcas <- rcas[,c("RCAID", "STHD_IP", "CHNK_IP", "LENGTH")]
    rcas$STHD_IP <- as.character(rcas$STHD_IP)
    rcas$CHNK_IP <- as.character(rcas$CHNK_IP)
    
    
    #rca <- read.csv(paste0(mainPath, "/", longBasin, "/", rcaName, ".csv"), stringsAsFactors = FALSE)
    
    
    
    # ext <- "Chinook"
    # 
    # if (ext != "Full") {
    #   ind <- apply(rcas, 1, function(x) x == ext)
    #   ANY <- apply(ind, 2, any)
    #   rcasTest <- rcas[ANY,]
    #   rcaList <- unique(rcasTest$RCAID)
    # } else{
    #   rcaList <- rcas$RCAID
    # }
    # 
    # 
    # totLen <- sum(rcasTest$LENGTH, na.rm=TRUE) 
    
   rcas <- subset(rcas, CHNK_IP == "Chinook") 
  #  rcas <- as.matrix(rcas)
  #  ind <- apply(rcas, 1, function(x) !any(is.na(x)))
  # rcas3 <- rcas[ind,]
  # rcas3 <- unique(rcas3)
  rcaList <- unique(rcas$RCAID)
  
  totLen <- sum(rcas$LENGTH, na.rm=TRUE) 
   
```
Animation output
```{r}

  fish = c("#C1CDCD", "#00FFFF", "#0000CD")
  fish <- rev(fish)

  names.out <- colnames(network@data[3:48])
  namesnum <- as.numeric(gsub(paste0("T", var, yrPath, "_"), "", colnames(network@data[3:48])))
```
Set dispPerc once at the begining
```{r}
  dispPerc <- numeric(96)

  sequ <- c(1:96) # 
  temp <- 20
  namer <- sprintf('%03d', sequ)
  table.out <- data.frame(Year=numeric(96), JulianDay=numeric(96), Length=numeric(96), Total=numeric(96), Percent=numeric(96))
  
```
read in the spatial data
```{r, message=FALSE}

  yrPath <- "15"
  yearPath <- "2015"
  modelPath <- paste0(mainPath, longBasin, "/", yearPath, "/", longVar)
  dataPath <- paste0(modelPath, longBasin, "/", yearPath, "/", longVar)
  outnetname <- paste0(basin, "_", yearPath, "_8D_", var)

  netin <- readOGR(dsn=modelPath, outnetname)
  #colnames(netin@data)[1] <- "RCAID"
 #netin@data$RCAID <- as.numeric(netin@data$RCAID)
  #netin@data$CHNK_IP <- as.character(netin@data$CHNK_IP)
  #network = netin[netin@data$CHNK_IP == "Chinook",]
  network = netin[netin$RCAID %in% rcaList,]
  #network@data <- network@data[,c(50,1:49)] 
  
```

reset sequence before running
```{r}
  for (i in 81:96) #June 10-Oct 15 2011 1:16, 2012 17:32, 2013 33:48, 2014 49:64, 2015 65:80, 2016 81:96  #21:36 
    {
      
      j <- i-60   # 2011 i+20, 2012 i+4, 2013 i-12, 2014 i-28, 2015 i-44, 2016 i-60
      #namey <- gsub(paste0("T", var, yrPath, "_"), "", colnames(network@data)[j])
     
      
      filename <- paste0(otherOutPath, "graphics/", sprintf('%03d', sequ[i]), ".png", sep="")
      png(filename=filename, res = 300, width = 1500, height = 1500, units = "px", bg="black")
      
      u <- length(which(network@data[,j]>temp)) 
      k <- dim(network@data)[1]
      tryThis <- which(network@data[,j]<temp) 
      subRCA <- network@data[tryThis, "RCAID"]
      subLen <- subset(rcas, RCAID %in% subRCA)
      percLen <- 100*(sum(subLen$LENGTH)/totLen)
      dispPerc[i] <- percLen
       
       table.out[i,1] <- yearPath
       table.out[i,2] <- namey[j-2]
       table.out[i,3] <- sum(subLen$LENGTH)
       table.out[i,4] <- totLen
       table.out[i,5] <- percLen
                         
      if(u< 1){
        fix3.colors <- rep("#0000CD",k)
      } else {
      fix3 <- classIntervals(network@data[,j], style = "fixed",fixedBreaks=c(0,19,20,25)) #change temp range for 
      fix3.colors <- findColours(fix3,pal=fish)
      }
      

      plot(network, col=fix3.colors, bg="black", fg="white")
      
      
    legend(x=grconvertX(c(0.78, 0.95), from='npc'),
             y=grconvertY(c(0.35, 0.55), from='npc'), fill = c("#0000CD", "#C1CDCD"), title="8-day mean max", legend = c("< 20 °C", "> 20 °C"), bty = "n", cex=.5, inset=c(.1,0), text.col="white");

      
      title(paste0("Available Chinook holding and spawning habitat in the ", nameBasin,", 10 June - 15 Oct, 2011-2016"), line=-0.1, adj=.80, col.main="white", col.sub="white", outer=FALSE, cex.main=0.6, cex.sub=0.5)
      mtext(paste0("Julian Day ", namey[j-2]),side =1, outer=TRUE, line=-4, col="white", cex=.5)
      mtext(paste0(yearPath),side =1, outer=TRUE, line=-3, col="white", cex=.75)
        
      #change xlim
       tmp2 <- subplot(
        plot(sequ[1:i], dispPerc[1:i], type="l", col="lightblue", bty="n", ylim=c(0,100), xlim=c(1,96), xlab="     2011    2012    2013    2014    2015    2016", ylab="", cex.lab=.85, cex.main=.9, main="Percent usable stream length", adj=0, line=.5, col.lab="white", col.main = "white", cex.axis=0.7, col.axis="white", bg="black", yaxp=c(0,100,2), xaxp=c(2011,2016,2)),
        
        x=grconvertX(c(0.02,0.45), from='npc'), 
        y=grconvertY(c(0.02, 0.20), from='npc'),
        size=c(1,1.5), vadj=0.5, hadj=0.5, 
        pars=list( mar=c(0,0,0,0)+0.1, cex=0.5))
        
      dev.off()
      
    }
```
Format and write out the table
```{r}
  
  colnames(table.out) <- c("Year", "JulianDay", "Length", "Total length", "Percent total length")
  
  table.out[,3:5] <- round(table.out[,3:5], digits=2)
  write.csv(table.out, file = paste0("Length_table_", basin, "_", temp, ".csv"), row.names = FALSE)
```
This system call builds an mpeg out of the still graphics
```{r}
setwd(paste0(otherOutPath, "/graphics/"))
  
  system('"C:/Program Files/ImageMagick-7.0.1-Q16/convert.exe" -delay 15 -morph 3 *.png Ent_Chinook_20.mpeg')
```
Find the peak low for graphing
```{r}
      

      m <- which.min(dispPerc)


```
```{r}
      i <- length(dispPerc)
      j <- m-44 # pull this from the appropriate year 2011 i+20, 2012 i+4, 2013 i-12, 2014 i-28, 2015 i-44, 2016 i-60
      
      namey <- namesnum[j]
      filename <- paste0(otherOutPath, "output/", basin, "_CHNK_", temp, "_still", ".png", sep="")
      png(filename=filename, res = 300, width = 1500, height = 1500, units = "px", bg="white")
      
      
      fix3 <- classIntervals(network@data[,j], style = "fixed",fixedBreaks=c(0,20,25)) #change ramp values as needed
      fix3.colors <- findColours(fix3,pal=fish)
      
      
      
      
      plot(network, col=fix3.colors, bg="white", fg="black")
      
      
    legend(x=grconvertX(c(0.78, 0.95), from='npc'),
             y=grconvertY(c(0.35, 0.55), from='npc'), fill = c("#0000CD", "#C1CDCD"), title="8-day mean max", legend = c("< 20 °C", "> 20 °C"), bty = "n", cex=.5, inset=c(.1,0), text.col="black");

      
      title(paste0("Available Chinook holding and spawning habitat in the ", nameBasin,", 2011-2016"), line=-0.1, adj=.80, col.main="black", col.sub="black", outer=FALSE, cex.main=0.6, cex.sub=0.5)
      mtext(paste0("Julian Day ", namey),side =1, outer=TRUE, line=-4, col="black", cex=.5)
      mtext(paste0(yearPath),side =1, outer=TRUE, line=-3, col="black", cex=.75)
        
       tmp2 <- subplot(
        plot(sequ[1:i], dispPerc[1:i], type="l", col="blue", bty="n", ylim=c(0,100), xlim=c(1,96), xlab="      2011     2012     2013     2014     2015     2016", ylab="", cex.lab=.8, cex.main=.9, main="Percent usable stream length", adj=0, line=.5, col.lab="black", col.main = "black", cex.axis=0.6, col.axis="black", bg="white", yaxp=c(0,100,2), xaxp=c(2011,2016,2)),
        #axis(1, at=1:6, labels = c("2011", "2012", "2013", "2014", "2015", "2016")),
        
        x=grconvertX(c(0.02,0.45), from='npc'), 
        y=grconvertY(c(0.02, 0.20), from='npc'),
        size=c(1,1.5), vadj=0.5, hadj=0.5, 
        pars=list( mar=c(0,0,0,0)+0.1, cex=0.5))
        
       op <- par(no.readonly=TRUE)
      par(tmp2)
      points(sequ[m], dispPerc[m], pch=16, col="red", cex=0.7)
      par(op)
      
      dev.off()
```
output just the percent / year plot
```{r}

    j <- length(dispPerc)  
    
    filename <- paste0(otherOutPath, "/output/", basin, "_CHNK_", temp, "_graph", ".png", sep="")
    png(filename=filename, res = 300, width = 1200, height = 1200, units = "px", bg="white")
    
    par(mar=c(4,4,4,4)+0.1)
  plot(sequ[1:j], dispPerc[1:j], type="l", col="blue", bty="n", ylim=c(0,110), xlim=c(1,96),
       
       xlab="       2011    2012    2013    2014    2015    2016", ylab="", cex.lab=.65, cex.main=.4, 
       main=paste0("Chinook holding and spawning habitat in the ", nameBasin, " under ", temp, " °C, 2011-2016 \n \n Percent usable stream length"), adj=0, line=0.1, col.lab="black", col.main = "black", 
       cex.axis=0.5, col.axis="black", bg="white", yaxp=c(0,100,2), xaxp=c(2011,2016,2))
    

```