---
title: "Code to output fish animations: 2 or 4 degree"
output: html_notebook
---

This set of R scripts processes logger data for predictive stream temperature modeling
Created: 21 Feb 2017
Used for all watersheds and all years by changing the basin names and year paths 

Stage setting:
```{r, message=FALSE}
library(timeSeries)
library(lattice)
library(foreign)
library(doBy)
library(qpcR)
library(pls)
library(boot)
library(Hmisc)
library(readxl)
library(lubridate)
library(zoo)
library(car)
library(gvlma)
library(ggplot2)
library(rgdal)
library(raster)
library(RColorBrewer)
library(classInt)
library(uuid)
library(plyr)
```
Processing stuff
```{r, message=FALSE, warning=TRUE}
  
  basin <- "Tuc"
  
  longBasin <- "Tucannon"
  nameBasin <- "Tucannon"
  
  mainPath <- paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/") 
  otherOutPath <- paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/FishMap/", longBasin, "/")
  
  
  var <- "Mx"
  longVar <- "Max"
  
  
  #gisPath <- paste0("D:/OneDrive/work/research/CHaMP/GIS/coverages/", longBasin)
  gisPath <- paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/EP_temp/", basin)
  
  namer <- c(1,9,17,25,33,41,49,57,65,73,81,89,97,105,113,121,129,137,145,153,161,169,177,185,193,201,209,217,225,233,241,249,257,265,273,281,289,297,305,313,321,329,337,345,353,361)
  namey <- sprintf('%03d', namer)
```
Parsing network extent
```{r}

    rcaName <- paste0("STDH_Ext")
    rca <- readOGR(dsn=gisPath, layer = rcaName)
    
    rcaList <- unique(rca$RCAID)
  
    totLen <- sum(rca$LENGTH, na.rm=TRUE) 
   
```
Animation output
```{r}

  fish = c("#C1CDCD", "#00FFFF", "#0000CD")
  #fish <- rev(fish)

  names.out <- colnames(network@data[3:48])
  namesnum <- as.numeric(gsub(paste0("T", var, yrPath, "_"), "", colnames(network@data[3:48])))
```
Set dispPerc once at the begining
```{r}
  dispPerc <- numeric(102)
  dispPerc2 <- numeric(102)
  
  sequ <- c(1:102) # 
  temp <- 2
  temp2 <- 4
  #namer <- sprintf('%03d', sequ)
  table.out <- data.frame(Year=numeric(102), JulianDay=numeric(102), Length=numeric(102), Total=numeric(102), Percent=numeric(102))
  
```
read in the spatial data
```{r, message=FALSE}

  yrPath <- "11"
  yearPath <- "2011"
  modelPath <- paste0(mainPath, longBasin, "/", yearPath, "/", longVar)
  dataPath <- paste0(modelPath, longBasin, "/", yearPath, "/", longVar)
  outnetname <- paste0(basin, "_", yearPath, "_8D_", var)

  netin <- readOGR(dsn=modelPath, outnetname)
  #colnames(netin@data)[1] <- "RCAID"
  #netin@data$RCAID <- as.numeric(netin@data$RCAID)
  #netin@data$CHNK_IP <- as.character(netin@data$CHNK_IP)
  #network = netin[netin@data$CHNK_IP == "Chinook",]
  network = netin[netin$RCAID %in% rcaList,]
  #network@data <- network@data[,c(50,1:49)] 
   
```
images
```{r}
  for (i in 86:102) # 2011 1:17, 2012 18:34, 2013 35:51, 2014 52:68, 2015 69:85, 2016 86:102;   7-23 
    {
      
      j <- i-79 # 2011 i+6, 2012 i-11, 2013 i-28, 2014 i-45, 2015 i-62, 2016 i-79
    
      filename <- paste0(otherOutPath, "graphics/", sprintf('%03d', sequ[i]), ".png", sep="")
      png(filename=filename, res = 300, width = 1500, height = 1500, units = "px", bg="black")
      
      u <- length(which(network@data[,j]>temp)) 
      k <- dim(network@data)[1]
      tryThis <- which(network@data[,j]>temp)
      subRCA <- network@data[tryThis, "RCAID"]
      subLen <- subset(rca, RCAID %in% subRCA)
      percLen <- 100*(sum(subLen$LENGTH)/totLen)
      dispPerc[i] <- percLen

      tryThis2 <- which(network@data[,j]>temp2)
      subRCA2 <- network@data[tryThis2, "RCAID"]
      subLen2 <- subset(rca, RCAID %in% subRCA2)
      percLen2 <- 100*(sum(subLen2$LENGTH)/totLen)
      dispPerc2[i] <- percLen2

       table.out[j,1] <- yearPath
       table.out[j,2] <- namey[i]
       table.out[j,3] <- sum(subLen$LENGTH)
       table.out[j,4] <- totLen
       table.out[j,5] <- percLen
                         
      if(u< 1){
        fix3.colors <- rep("#0000CD",k)
      } else {
      fix3 <- classIntervals(network@data[,j], style = "fixed",fixedBreaks=c(0,2,4,25)) #change temp range as needed
      fix3.colors <- findColours(fix3,pal=fish)
      }
      

      plot(network, col=fix3.colors, bg="black", fg="white")
      
      
    legend(x=grconvertX(c(0.02,0.2), from='npc'), 
        y=grconvertY(c(0.45, 0.55), from='npc'), fill = c("#0000CD", "#00FFFF", "#C1CDCD"), title="8-day mean max", legend = c("> 4 °C", "2-4 °C", "< 2 °C"), bty = "n", cex=.5, inset=c(.1,0), text.col="white");

    legend(x=grconvertX(c(0.39, 0.49), from='npc'),
             y=grconvertY(c(0.0, 0.08), from='npc'), fill = c("lightblue", "cyan2"), legend = c("> 2 °C", "> 4 °C"), bty = "n", cex=.4, inset=c(0,0), text.col="white");
      
      title(paste0("Available steelhead spawning habitat in the ", nameBasin,", 1 Feb - 15 June, 2011-2016"), line=-0.1, adj=.80, col.main="white", col.sub="white", outer=FALSE, cex.main=0.6, cex.sub=0.5)
      mtext(paste0("Julian Day ", namey[j-2]),side =1, outer=TRUE, line=-4, col="white", cex=.5)
      mtext(paste0(yearPath),side =1, outer=TRUE, line=-3, col="white", cex=.75)
        
      #change xlim
       tmp2 <- subplot(
        plot(sequ[1:i], dispPerc[1:i], type="l", col="lightblue", bty="n", ylim=c(0,100), xlim=c(1,102), xlab="      2011    2012    2013    2014    2015    2016", ylab="", cex.lab=.8, cex.main=.9, main="Percent usable stream length", adj=0, line=.5, col.lab="white", col.main = "white", cex.axis=0.6, col.axis="white", bg="black", yaxp=c(0,100,2), xaxp=c(2011,2016,2)),
        
        x=grconvertX(c(0.02,0.45), from='npc'), 
        y=grconvertY(c(0.02, 0.20), from='npc'),
        size=c(1,1.5), vadj=0.5, hadj=0.5, 
        pars=list( mar=c(0,0,0,0)+0.1, cex=0.5))
       
       tmp2 <- subplot(
        plot(sequ[1:i], dispPerc2[1:i], type="l", col="cyan2", bty="n", ylim=c(0,100), xlim=c(1,102), xlab="      2011    2012    2013    2014    2015    2016", ylab="", cex.lab=.8, cex.main=.9, main="Percent usable stream length", adj=0, line=.5, col.lab="white", col.main = "white", cex.axis=0.6, col.axis="white", bg="black", yaxp=c(0,100,2), xaxp=c(2011,2016,2)),
        
        x=grconvertX(c(0.02,0.45), from='npc'), 
        y=grconvertY(c(0.02, 0.20), from='npc'),
        size=c(1,1.5), vadj=0.5, hadj=0.5, 
        pars=list( mar=c(0,0,0,0)+0.1, cex=0.5))
        
      dev.off()
      
    }
    
  
```
This system call builds an mpeg out of the still graphics
```{r}
setwd(paste0(otherOutPath, "/graphics/"))
  
  system('"C:/Program Files/ImageMagick-7.0.1-Q16/convert.exe" -delay 15 -morph 3 *.png Tuc_STHD_4.mpeg')
```
Find the peak low for graphing
```{r}
      

      m <- which.min(dispPerc)
      #make sure the correct year's network is loaded

```
write out the graphic
```{r}
      i <- length(dispPerc)
      j <- m+6 # pull this from the appropriate year 2011 i+6, 2012 i-11, 2013 i-28, 2014 i-45, 2015 i-62, 2016 i-79
      
      namey <- namesnum[j]
      filename <- paste0(otherOutPath, "output/", basin, "_STHD_", temp2, "_still", ".png", sep="")
      png(filename=filename, res = 300, width = 1500, height = 1500, units = "px", bg="white")
      
      
      fix3 <- classIntervals(network@data[,j], style = "fixed",fixedBreaks=c(0,2,4,25)) #change temp range as needed
      fix3.colors <- findColours(fix3,pal=fish)
      
      
      
      
      plot(network, col=fix3.colors, bg="white", fg="black")
      
      
    legend(x=grconvertX(c(0.02,0.2), from='npc'), 
        y=grconvertY(c(0.45, 0.55), from='npc'), fill = c("#0000CD", "#00FFFF", "#C1CDCD"), title="8-day mean max", legend = c("> 4 °C", "2-4 °C", "< 2 °C"), bty = "n", cex=.5, inset=c(.1,0), text.col="black");

    
      title(paste0("Available Steelhead spawning habitat in the ", nameBasin,", 1 Feb - 15 June, 2011-2016"), line=-0.1, adj=.80, col.main="black", col.sub="black", outer=FALSE, cex.main=0.6, cex.sub=0.5)
      mtext(paste0("Julian Day ", namey),side =1, outer=TRUE, line=-4, col="black", cex=.5)
      mtext(paste0(yearPath),side =1, outer=TRUE, line=-3, col="black", cex=.75)
        
       tmp2 <- subplot(
        plot(sequ[1:i], dispPerc[1:i], type="l", col="lightblue", bty="n", ylim=c(0,100), xlim=c(1,102), xlab="      2011    2012    2013    2014    2015    2016", ylab="", cex.lab=.8, cex.main=.9, main="Percent usable stream length", adj=0, line=.5, col.lab="black", col.main = "black", cex.axis=0.6, col.axis="black", bg="white", yaxp=c(0,100,2), xaxp=c(2011,2016,2)),
        
        x=grconvertX(c(0.02,0.45), from='npc'), 
        y=grconvertY(c(0.02, 0.20), from='npc'),
        size=c(1,1.5), vadj=0.5, hadj=0.5, 
        pars=list( mar=c(0,0,0,0)+0.1, cex=0.5))
       
        op <- par(no.readonly=TRUE)
      
      
       tmp2 <- subplot(
        plot(sequ[1:i], dispPerc2[1:i], type="l", col="cyan2", bty="n", ylim=c(0,100), xlim=c(1,102), xlab="      2011    2012    2013    2014    2015    2016", ylab="", cex.lab=.8, cex.main=.9, main="Percent usable stream length", adj=0, line=.5, col.lab="black", col.main = "black", cex.axis=0.6, col.axis="black", bg="white", yaxp=c(0,100,2), xaxp=c(2011,2016,2)),
        
        x=grconvertX(c(0.02,0.45), from='npc'), 
        y=grconvertY(c(0.02, 0.20), from='npc'),
        size=c(1,1.5), vadj=0.5, hadj=0.5, 
        pars=list( mar=c(0,0,0,0)+0.1, cex=0.5))
        
       op <- par(no.readonly=TRUE)
      par(tmp2)
      points(sequ[m], dispPerc[m], pch=16, col="red", cex=0.7)
      par(op)
      
      dev.off()
```
output just the percent / year plot
```{r}

    j <- length(dispPerc)  
    
    filename <- paste0(otherOutPath, "/output/", basin, "_STHD_", temp, "_graph", ".png", sep="")
    png(filename=filename, res = 300, width = 1200, height = 1200, units = "px", bg="white")
    
    par(mar=c(4,4,4,4)+0.1)
  plot(sequ[1:j], dispPerc[1:j], type="l", col="lightblue", bty="n", ylim=c(0,110), xlim=c(1,102),
       
       xlab="      2011      2012       2013       2014       2015       2016", ylab="", cex.lab=.5, cex.main=.4, 
       main=paste0("Steelhead spawning habitat in the ", nameBasin, " under ", temp, " & ", temp2, " °C, 1 Feb - 15 June, 2011-2016 \n \n Percent usable stream length"), adj=0, line=0.1, col.lab="black", col.main = "black", 
       cex.axis=0.5, col.axis="black", bg="white", yaxp=c(0,100,2), xaxp=c(2011,2016,2))
  points(sequ[1:i], dispPerc2[1:i], type="l", col="cyan2") 
  legend(x=grconvertX(c(0.84, 0.99), from='npc'),
         y=grconvertY(c(0.0, 0.1), from='npc'),
         fill = c("lightblue", "cyan2"), legend = c("> 2 °C", "> 4 °C"), bty = "n", cex=.4, text.col="black");

```