---
title: "Upper Grande Ronde RV modeling - Mean temp"
output: html_notebook
---
NBCD Basal Area Weight [BAW] estimated veg height [EVH] in m

```{r, message=FALSE}
library(timeSeries)
library(lattice)
library(foreign)
library(doBy)
library(qpcR)
library(pls)
library(boot)
library(Hmisc)
library(readxl)
library(lubridate)
library(zoo)
library(car)
library(gvlma)
library(ggplot2)
library(foreign)
library(DT)
library(data.table)
library(rgdal)
library(raster)
library(uuid)
```
```{r}
  basin <- "UGR"
  longBasin <- "UpperGrandeRonde"
  
  dataPath <- "D:/OneDrive/work/research/CHaMP/CHaMP_data/RiparianVeg/"
  mainPath <- paste0("D:/OneDrive/work/research/CHaMP/CHaMP_data/", longBasin)
  
  gisPath <- "D:/OneDrive/work/research/CHaMP/GIS/coverages"
  
  CRBproj <-  "+proj=aea +lat_1=20 +lat_2=60 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0"
```
# ### Process spatial data ###
# in Arc clip the veg rasters to the vbet extent
# Read in veg rasters, convert to points
```{r}

  
  BpS <- raster(paste0(gisPath, longBasin, "/", basin, "_Bps_vbet"))
  Baw <- raster(paste0(gisPath, longBasin, "/", basin, "_Baw_vbet"))
  
  BpSpoints <- rasterToPoints(BpS, spatial=TRUE)
  
``` 
# Basic geospatial processing of the veg grids - done once
# intersect the Potentiatl veg points with the current veg raster
```{r}
  
  Bawpoints <- extract(Baw, BpSpoints)
  
  Bawpoints <- as.data.frame(Bawpoints)
  
  xy <- BpSpoints@coords
  Bawpoints$x <- xy[,1]
  Bawpoints$y <- xy[,2]
  write.dbf(Bawpoints, file="Bawpoints.dbf")
   
           
  outptsname <- paste0(basin, "_Bps_pts") 
  writeOGR(obj=BpSpoints, dsn=gisPath, layer = paste0(outptsname), driver="ESRI Shapefile", overwrite_layer = TRUE) 
```
# Read those points into Arc, intersected with the RCAs, wrote out as .dbf
# This part calculates the mean of the BAW EVH for each RCA
```{r}

  baw_rca <- read.dbf(paste0(basin, "_Baw_RCAID.dbf"))
  colnames(baw_rca) <- c("Cur_EVH", "RCAID")
  
  bps_rca <- read.dbf(paste0(basin, "_BpS_RCAID.dbf"))
  colnames(bps_rca) <- c("Pot_EVH", "RCAID")
  
  rcas <- unique(baw_rca$RCAID)
  rca_zonal <- matrix(ncol=3, nrow=length(rcas))
 
  for(i in 1:length(rcas))	
    {
      RCAID <- rcas[i]
      
      pixels <- baw_rca[baw_rca$RCAID == RCAID, "Cur_EVH"]
      zonal_mn <- mean(pixels, na.rm = TRUE)
      rca_zonal[i,1] <- zonal_mn
      
      pixels <- bps_rca[bps_rca$RCAID == RCAID, "Pot_EVH"]
      zonal_mn <- mean(pixels, na.rm = TRUE)
      rca_zonal[i,2] <- zonal_mn
      
      rca_zonal[i,3] <- RCAID
    
    }
  
  
  colnames(rca_zonal) <- c("Cur_EVH", "Pot_EVH", "RCAID")
  rca_zonal <- as.data.frame(rca_zonal)
  rca_zonal$RCAID <- rcas
  
  write.csv(rca_zonal, paste0(basin, "_RV_RCA_zonal", ".csv"), row.names = FALSE)
```
# define outputs dataframe
```{r}
  
  outputStats <- data.frame(mup=NULL)
```
# define variables to be modeled 
```{r}
  longVar <- "Mean"
  var <- "Mn"
```
# prepping output data structure
```{r}
  rca_zonal <- read.csv(paste0(basin, "_RV_RCA_zonal", ".csv"), stringsAsFactors = FALSE)

  gisPath <- paste0("D:/OneDrive/work/research/CHaMP/GIS/coverages/", longBasin)
  
  netname <- paste0(basin, "_STHD_net")
  
  network <- readOGR(dsn=gisPath, layer = netname)
  
  
                                   
  fishrcas <- unique(network@data$RCAID)
  
  rcas <- fishrcas[fishrcas %in% rca_zonal$RCAID]
  
  Alldata <- data.frame(mup=NULL)
```
# This section is repeated for each year
# set year
```{r}
  yrPath <- 11
  yearPath <- "2011"
  
  
  LST.in <- read.dbf(paste0(mainPath, "/", "LST", yrPath, "_", basin, "_RCA.dbf"))  
  colnames(LST.in)[47] <-"RCAID"
  
  Predt.in <- read.dbf(paste0(mainPath, "/", yearPath, "/", longVar, "/", "predt", yearPath, "_", basin, "_8D_", var, ".dbf"))
  
  rcas <- rcas[rcas %in% Predt.in$RCAID]
  model.data <- data.frame(mup=NULL)
 
  
  for (i in rcas) 
    { 
          RCAID <- i
          
          Pred.site <- unlist(Predt.in[Predt.in$RCAID == RCAID,23:33])
          Pred.Mx <- max(Pred.site)
          Pred.Mn <- mean(Pred.site)
    
          LST.site <- unlist(LST.in[LST.in$RCAID == RCAID,23:33])
          mnLST <- mean(LST.site)
          mxLST <- max(LST.site)
          rngLST <- max(LST.site) - min(LST.site)
          year <- yearPath
          Cur.EVH <- rca_zonal[rca_zonal$RCAID == RCAID,"Cur_EVH"]
          Pot.EVH <- rca_zonal[rca_zonal$RCAID == RCAID,"Pot_EVH"]
          
          data <- data.frame(RCAID=RCAID, PredMxMn=Pred.Mx, PredMnMn=Pred.Mn, mnLST=mnLST, mxLST=mxLST, rngLST=rngLST, year=year, Cur_EVH=Cur.EVH, Pot_EVH=Pot.EVH, VegDif=Pot.EVH-Cur.EVH)
          model.data <- rbind(model.data, data)
         
    }
  

  Alldata <- rbind(Alldata, model.data)
```
# Parse out restorable sites
```{r}
  
  RestData <- Alldata[Alldata$VegDif > 0,]
  ind <- apply(RestData, 1, function(x) !any(is.na(x)))
  RestData <- RestData[ind,]

```
#Correlation matrix
```{r}
  cor.full <- RestData[c(2:6,8:9)]
  cor(cor.full)
```

# plot linear relationship between temp and veg - max mean
```{r}

  {plot(RestData$Cur_EVH, RestData$PredMxMn, main = paste0("Temp v current EVH all years, max mean"))

  abline(lm(RestData$PredMxMn ~ RestData$Cur_EVH), col="blue")}
```
# Models
# ### Max mean
```{R}
  y <- RestData$PredMxMn
  x <- RestData$Cur_EVH
  xPot <- RestData$Pot_EVH
  xPot <- as.data.frame(xPot)
  colnames(xPot) <- "x"
```
```{r}
  mod <- lm(y ~ x)
  sum_mod <- summary(mod)
  sum_mod
  
```
# add the potential temp to the data frame
```{r}
    
  pred.y <- predict(mod, newdata = xPot)

  RestData$Pot_MxMn <- pred.y
```
# mean temp difference
```{r}
  data <- data.frame(PotDifMxMn=mean(RestData$PredMxMn - RestData$Pot_MxMn))
  outputStats <- rbind(outputStats, data)
  
```
# ### Mean mean
# plot linear relationship between temp and veg - mean mean
```{r}

  {plot(RestData$Cur_EVH, RestData$PredMnMn, main = paste0("Temp v current EVH all years, mean mean"))

  abline(lm(RestData$PredMnMn ~ RestData$Cur_EVH), col="blue")}
```
 # model
```{R}
  y <- RestData$PredMnMn
  x <- RestData$Cur_EVH
  xPot <- RestData$Pot_EVH
  xPot <- as.data.frame(xPot)
  colnames(xPot) <- "x"
```
```{r}
  mod <- lm(y ~ x)
  sum_mod <- summary(mod)
  sum_mod
```
```{r}
  pred.y <- predict(mod, newdata = xPot)
 
  RestData$Pot_MnMn <- pred.y
```
# mean temp difference
```{r}
  data <- data.frame(PotDifMnMn=mean(RestData$PredMnMn - RestData$Pot_MnMn))
  outputStats <- cbind(outputStats, data)
  
```
# annual parse
# All data
```{r}
  y2011 <- Alldata[Alldata$year == 2011,]
  y2012 <- Alldata[Alldata$year == 2012,]
  y2013 <- Alldata[Alldata$year == 2013,]
  y2014 <- Alldata[Alldata$year == 2014,]
  y2015 <- Alldata[Alldata$year == 2015,]
```
# Restoration site data
```{r}
  y2011rest <- RestData[RestData$year == 2011, c("RCAID", "Pot_MxMn", "Pot_MnMn")]
  y2012rest <- RestData[RestData$year == 2012, c("RCAID", "Pot_MxMn", "Pot_MnMn")]
  y2013rest <- RestData[RestData$year == 2013, c("RCAID", "Pot_MxMn", "Pot_MnMn")]
  y2014rest <- RestData[RestData$year == 2014, c("RCAID", "Pot_MxMn", "Pot_MnMn")]
  y2015rest <- RestData[RestData$year == 2015, c("RCAID", "Pot_MxMn", "Pot_MnMn")]
```
# Add potential temp to full network temp estimates
```{r}
 
  y2011out <- merge(y2011, y2011rest, by="RCAID", all.x=TRUE)
  y2011out$Pot_MxMn[is.na(y2011out$Pot_MxMn)] <- y2011out$PredMxMn[is.na(y2011out$Pot_MxMn)]
  y2011out$Pot_MnMn[is.na(y2011out$Pot_MnMn)] <- y2011out$PredMnMn[is.na(y2011out$Pot_MnMn)]

  y2012out <- merge(y2012, y2012rest, by="RCAID", all.x=TRUE)
  y2012out$Pot_MxMn[is.na(y2012out$Pot_MxMn)] <- y2012out$PredMxMn[is.na(y2012out$Pot_MxMn)]
  y2012out$Pot_MnMn[is.na(y2012out$Pot_MnMn)] <- y2012out$PredMnMn[is.na(y2012out$Pot_MnMn)]
  
  y2013out <- merge(y2013, y2013rest, by="RCAID", all.x=TRUE)
  y2013out$Pot_MxMn[is.na(y2013out$Pot_MxMn)] <- y2013out$PredMxMn[is.na(y2013out$Pot_MxMn)]
  y2013out$Pot_MnMn[is.na(y2013out$Pot_MnMn)] <- y2013out$PredMnMn[is.na(y2013out$Pot_MnMn)]
  
  y2014out <- merge(y2014, y2014rest, by="RCAID", all.x=TRUE)
  y2014out$Pot_MxMn[is.na(y2014out$Pot_MxMn)] <- y2014out$PredMxMn[is.na(y2014out$Pot_MxMn)]
  y2014out$Pot_MnMn[is.na(y2014out$Pot_MnMn)] <- y2014out$PredMnMn[is.na(y2014out$Pot_MnMn)]
  
  y2015out <- merge(y2015, y2015rest, by="RCAID", all.x=TRUE)
  y2015out$Pot_MxMn[is.na(y2015out$Pot_MxMn)] <- y2015out$PredMxMn[is.na(y2015out$Pot_MxMn)]
  y2015out$Pot_MnMn[is.na(y2015out$Pot_MnMn)] <- y2015out$PredMnMn[is.na(y2015out$Pot_MnMn)]
  
  RestDataOut <- RestData[, c("RCAID", "Pot_MxMn", "Pot_MnMn")]
  AlldataOut <- merge(Alldata, RestDataOut, all.x=TRUE)
  AlldataOut$Pot_MxMn[is.na(AlldataOut$Pot_MxMn)] <- AlldataOut$PredMxMn[is.na(AlldataOut$Pot_MxMn)]
  AlldataOut$Pot_MnMn[is.na(AlldataOut$Pot_MnMn)] <- AlldataOut$PredMnMn[is.na(AlldataOut$Pot_MnMn)]
```
write it out
```{r}
  write.table(x=AlldataOut, append=F,row.names=F, file = paste0("11_15/", longVar, "/", basin, "_11-15_pot_Mn_temp.csv"), sep = ",", col.names=T)

  write.table(x=y2011out, append=F,row.names=F, file = paste0("2011/", longVar, "/", basin, "_2011_pot_Mn_temp.csv"), sep = ",", col.names=T)

  write.table(x=y2012out, append=F,row.names=F, file = paste0("2012/", longVar, "/", basin, "_2012_pot_Mn_temp.csv"), sep = ",", col.names=T)
  
  write.table(x=y2013out, append=F,row.names=F, file = paste0("2013/", longVar, "/", basin, "_2013_pot_Mn_temp.csv"), sep = ",", col.names=T)
  
  write.table(x=y2014out, append=F,row.names=F, file = paste0("2014/", longVar, "/", basin, "_2014_pot_Mn_temp.csv"), sep = ",", col.names=T)
  
  write.table(x=y2015out, append=F,row.names=F, file = paste0("2015/", longVar, "/", basin, "_2015_pot_Mn_temp.csv"), sep = ",", col.names=T)
  
  write.csv(outputStats, file = paste0("11_15/", longVar, "/", basin, "_11-15_mean_Diff.csv"), row.names=FALSE)
```
# Basin mean change in stream temperature (output to screen)
```{r, message=FALSE}

  outputStats
```
Geospatial data output
```{r, message=FALSE}

  gisBasin <- "Grand_Ronde"

  gisPath <- paste0("D:/OneDrive/work/research/CHaMP/GIS/coverages/", gisBasin)
  
  netname <- paste0(basin, "_STHD_net")
  
  network <- readOGR(dsn=gisPath, layer = netname)
  
```
# merging and writing out
```{r}
  
  longVar <- "Mean"
  var <- "Mn"
  yearPath <- "2015"

  outPath <- paste0(mainPath, "/RipVeg/",yearPath,"/",longVar)
  
  potTemp <- read.csv(paste0(outPath, "/", basin, "_", yearPath, "_pot_", var, "_temp.csv"), stringsAsFactors = FALSE)
  potTemp <- potTemp[,-12]
  
  netOut<- merge(network, potTemp, by = "RCAID", all.x=FALSE)                    
                      
  outnetname <- paste0(basin, "_", yearPath, "_Pot_", var, "_temp")
  
  writeOGR(obj=netOut, dsn=outPath, layer = paste0(outnetname), driver="ESRI Shapefile", overwrite_layer = TRUE)
```
This part generates the project.rs.xml file 
```{r, message=FALSE}

Realizguid = UUIDgenerate(F)

now <- Sys.Date()

modelPath <- paste0(mainPath, "/RipVeg/", yearPath, "/", longVar, "/")
                    
capVar <- "MEAN"

nameBasin <- "Upper Grande Ronde"

```
Start writing project.rs.xml file here
```{r}

cat("", file=paste(modelPath,"project.rs.xml",sep=""))

cat(paste("","<?xml version=\"1.0\" encoding=\"utf-8\"?>
<Project xmlns:xsi=\"http://www.w3.org/2001/XMLSchema-instance\"
  xsi:noNamespaceSchemaLocation=\"https://raw.githubusercontent.com/Riverscapes/Program/master/Project/XSD/V1/Project.xsd\">

  <Name>potential_stream_temperature_project</Name>
  <ProjectType>STREAMTEMPPOT",capVar,"</ProjectType>

  <MetaData>
    <!--This first metadata exists only to place this project in the riverscapes project-->
    <Meta name=\"description\">Summer mean and max potential stream temperature derived from potential riparian vegetation height</Meta>
    <Meta name=\"HUCID\">17060201</Meta>
		<Meta name=\"Region\">CRB</Meta>
    <Meta name=\"Watershed\">",nameBasin,"</Meta>
    <Meta name=\"Year\">", yearPath,"</Meta>
  </MetaData>

 <Realizations>
    <StreamTemperature guid=\"",Realizguid,"\" id=\"streamtemp\" dateCreated=\"",now,"\" productVersion=\"1.0\">
      <Name>Potential Stream Temperature for ",nameBasin, " ",yearPath,"</Name>

      <MetaData>
        <!--This next metadata relates to this particular realization-->
        <Meta name=\"Current_vegetation_dataset\">https://www.usna.edu/Users/oceano/pguth/md_help/html/nbcd.htm</Meta>
        <Meta name=\"Potential_vegetation_dataset\">https://www.landfire.gov/NationalProductDescriptions24.php</Meta>
        <Meta name=\"Current_temperature_estimates\">https://github.com/SouthForkResearch/StreamTemperature/wiki</Meta>
        <Meta name=\"Code_wiki\">https://github.com/SouthForkResearch/StreamTemperature/wiki</Meta>
      </MetaData>

    <Analyses>
      <Analysis>
        <Name>Stream Temp Analysis</Name>
          <Outputs>

            <Vector id=\"network\">
              <Name>Network_estimate_shapefile</Name>
              <Path>",basin,"_",yearPath,"_Pot_",var,"_temp",".shp</Path>
              <MetaData>
                <Meta name=\"description\">Shapefile of network with summer mean mean and max mean potential temperature estimates</Meta>
              </MetaData>
            </Vector>

            <CSV id=\"estimates\">
              <Name>Potential_temp_estimates_csv</Name>
              <Path>",basin, "_", yearPath,"_pot_",var,"_temp.csv</Path>
              <MetaData>
                <Meta name=\"description\">csv version of the potential temp estimates</Meta>
              </MetaData>
            </CSV>

          </Outputs>
        </Analysis>
      </Analyses>
    </StreamTemperature>
  </Realizations>
</Project>
",sep=""), file=paste(modelPath,"project.rs.xml",sep=""), append=T)

```
Still graphic output for wiki or web or wev
```{r}

  yearPath <- "2015"
  var <- "Mn"
  longVar <- "Mean"
  
  outPath <- paste0(mainPath, "/RipVeg/",yearPath,"/",longVar)
  
  outnetname <- paste0(basin, "_", yearPath, "_Pot_", var, "_temp")
  
  network <- readOGR(dsn=outPath, layer = outnetname)
```
```{r}
  
seis = c("#AA0000", "#D00000", "#F70000", "#FF1D00", "#FF4400", "#FF6A00", "#FF9000", "#FFB700", "#FFDD00", "#FFE200", "#BDFF0C", "#73FF1A", "#3FFA36", "#16F45A", "#00D08B", "#0087CD", "#0048FA", "#0024E3")
  seis <- rev(seis)
  
  i <- 5  
  
  
    fix3 <- classIntervals(network@data[,i], n = 12, style = "fixed",fixedBreaks=c(-1,2,4,6,8,10,12,14,16,18,20,22))
    fix3.colors <- findColours(fix3,pal=seis)
        
  filename <- paste0(outPath, "/graphics/", basin, "_", yearPath, "_cur_mean_", var, ".png", sep="")
    png(filename=filename, res = 300, width = 1500, height = 1500, units = "px", bg="white")
    
  
        
        plot(network, col=fix3.colors, bg="white", fg="black")
        
        
        legend("bottomleft", fill = attr(fix3.colors, "palette"), title="째C",legend = c("0-6","6-8","8-10","10-12","12-14","14-16","16-18","18-20", "20-22", "22+"), bty = "n", cex=.5, inset=c(0,0), text.col="black");
      
        title(paste0(longBasin, " current condition summer Mean ", longVar, " (째C)"), line=-0.2, adj=0.1, col.main="black", col.sub="black", outer=FALSE, cex.main=0.5)
        
       
```
```{r}
  
seis = c("#AA0000", "#D00000", "#F70000", "#FF1D00", "#FF4400", "#FF6A00", "#FF9000", "#FFB700", "#FFDD00", "#FFE200", "#BDFF0C", "#73FF1A", "#3FFA36", "#16F45A", "#00D08B", "#0087CD", "#0048FA", "#0024E3")
  seis <- rev(seis)
  
  i <- 14  
  
  
    fix3 <- classIntervals(network@data[,i], n = 12, style = "fixed",fixedBreaks=c(-1,2,4,6,8,10,12,14,16,18,20,22))
    fix3.colors <- findColours(fix3,pal=seis)
        
  filename <- paste0(outPath, "/graphics/", basin, "_", yearPath, "_pot_mean_", var, ".png", sep="")
    png(filename=filename, res = 300, width = 1500, height = 1500, units = "px", bg="white")
    
  
        
        plot(network, col=fix3.colors, bg="white", fg="black")
        
        
        legend("bottomleft", fill = attr(fix3.colors, "palette"), title="째C",legend = c("0-6","6-8","8-10","10-12","12-14","14-16","16-18","18-20", "20-22", "22+"), bty = "n", cex=.5, inset=c(0,0), text.col="black");
      
        title(paste0(longBasin, " potential condition summer Mean ", longVar, " (째C)"), line=-0.2, adj=0.1, col.main="black", col.sub="black", outer=FALSE, cex.main=0.5)
        
       
```
